Dynamic Knapsack Problem

### 2021-07-23 v2-Manuscript/Manuscript.tex
adjusting pricing

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
	\begin{alignat}{10}
		& ul'_{p} 
			&& = \hat{ul}_{p} + ued_{p} \quad 
			&& \forall p
	\end{alignat}

@@

\subsection{Costs}
Cost will come from 4 sources:  
\begin{itemize} 
	\item waiting ($cw$)
	\item rescheduling ($cc$)
	\item scheduling ($cs$)
	\item resource violation ($M$)
\end{itemize}

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
				prevent infinite reschedules} + \\
	&	&&	+
				\overbrace{
					\sum_{tmdc} cs^{t} (sc_{tmdc})
				}^\text{Prefer earlier appointments} \\ 
	&	&&  +
			\overbrace{
				(1.5cc) \sum_{
				\substack{tt`mdc \\ t' > t}} 
				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
			\overbrace{ 
				(0.5cc) \sum_{
				\substack{tt`mdc \\ t' < t}}
				rsc_{tt'mdc}}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

>>>>

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
	\begin{alignat}{10}
		& ul'_{p} 
			&& = \hat{ul}_{p} + ued_{p} \quad 
			&& \forall p \in \{ \text{Carry Over}\} \\
		& ul'_{p} 
			&& = ued_{p} \quad 
			&& \forall p \in \{ \text{Non Carry Over}\} 
	\end{alignat}

@@

\subsection{Costs}
Cost will come from 4 sources:  
\begin{itemize} 
	\item waiting ($cw$)
	\item rescheduling ($cc$) 
	\item scheduling ($cs_{t} = \sum_{t}cw^{t}$)
	\item resource violation ($M$)
\end{itemize}

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{
				\sum_{tmdc} cs_{t} (sc_{tmdc})
			}^\text{Prefer earlier appointments} \\ 
	&	&&  +
			\overbrace{
				\sum_{
				\substack{tt`mdc \\ t' > t}} 
				(cs_{t'-t} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
			\overbrace{ 
				\sum_{
				\substack{tt`mdc \\ t' < t}}
				(cs_{t-t'} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}
